A Transactional Memory System for Parallel Python

### 2014-06-06 talk/dls2014/paper/paper.tex
acks

\keywords
\remi{missing keywords}

@@

\cfbolz{you need to describe when and how to re-share pages}

@@

\acks
\remi{cfbolz, felber, marlier, fäs, mastoras}

>>>>

\keywords
transactional memory, global interpreter lock, dynamic language,
python, virtual machine

@@

@@

\acks
We would like to thank the following people for their valuable
inputs and the many fruitful discussions: Carl F. Bolz, Michael Faes,
Pascal Felber, Patrick Marlier, and Aristeidis Mastoras.
